### 2020-08-28 README.Rmd
remove st_as_sf since now in compute_growth

bw_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(bw_census_2008, bw_census_2014, id) %>%
  mutate(sp = to_any_case(sp)) %>%
  # Convert data frame to sf object DA note: should compute_growth do this??
  st_as_sf(coords = c("gx", "gy")) %>%
  # drop stemID
  select(-stemID)

@@

scbi_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>%
  # they are mesuaring in mm while we are measuring in cm!!!
  mutate(growth = growth/10) %>%
  st_as_sf(coords = c("gx", "gy"))

>>>>

bw_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(bw_census_2008, bw_census_2014, id) %>%
  mutate(sp = to_any_case(sp)) %>%
  # drop stemID
  select(-stemID)

@@

scbi_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>%
  # they are mesuaring in mm while we are measuring in cm!!!
  mutate(growth = growth/10)
